### 2021-04-07 notes/notes.tex
Minor changes to pars. Added some notes on simulations

\subsection{Fixed force value}
In this version, the force field is assumed to have a fixed value which the
agent tries to infer. The agent's uncertainty on this inference is reflected on
the parameters of the posterior over the force directly. For simplicity, we
assume that the priors (and posteriors) are normal with mean and standard
deviation to be updated at every time step. Therefore, the posterior over the
magnitude of the force for each context is given by:
\begin{equation}
q_t(\gamma) = N(\mu_{\gamma}, \sigma_\gamma)
\end{equation}
where $q_t(\gamma)$ is the posterior of the magnitude $\gamma$ of the force
field distribution after the observations at time $t$, and $\mu_\gamma$ and
$\sigma_\gamma$ are the inferred parameters of the distribution.

@@

\subsection{Fixed-$\sigma$ model}
In this model, the force at each trial is assumed to be sampled from a normal
distribution and the mean of this distribution is inferred from the
observations, while the standard deviation is assumed to be known. The mean of
the force is assumed to also be normal with unknown mean and standard
deviation:
\begin{align}
  p(\gamma) &= N(\mu_t, \sigma) \\
  p(\mu_t) &= N(\mu_mu, \sigma_\mu)
\end{align}
In this manner, the uncertainty for this agent is at the level of the estimate
of the parameters of the force field, as opposed to being directly on the
force. Because the priors for $\mu_\mu$ are normal and the standard deviation
$\sigma$ (not $\sigma_mu$) is known, the update equations are given by:
\begin{align}
  \mu_\mu &= \frac{\sigma^2}{\sigma^2 + \sigma_\mu^2}\mu_\mu + \frac{\sigma_\mu^2}{\sigma^2 + \sigma_\mu^2} x \\
  \sigma_\mu &= \frac{\sigma^2\sigma_\mu^2}{\sigma^2 + \sigma_\mu^2}
\end{align}
where $x$ is the observation.

\subsection{Full uncertainty}
In this version, we will assume that for each context, the agent's belief over
the magnitude of the force is given by a normal distribution:
\begin{equation}
p(\gamma) = N(\mu_f, \sigma_f) \label{eqn:data-dist}
\end{equation}
where $\mu_f$ and $\sigma_f$ are parameters to be estimated at each
trial. Before the experiment begins, the agent will have a prior distribution
over these parameters. A standard Bayesian approach is to choose NormalGamma
priors:
\begin{equation}
p(\mu_f, \sigma_f) = NG(\mu_0, \nu_0, \alpha_0, \beta_0)
\end{equation}
where $\mu_0, \nu_0, \alpha_0$ and $\beta_0$ are free hyperparameters of the
model. Because participants are told that there are three contexts (baseline,
left and right), we assume the following hyperparameter values:
\begin{align} \mu_f^{(0)} &= (0, -1, 1) \\
  \nu_f^{(0)} &= 0.1 \\
  \alpha_f^{(0)} &= 1 \\
  \beta_f^{(0)} &= 0.5
\end{align}
Note that $\mu_f^{(0)}$ is different for each context and is thus
provided as a vector $(0, -1, 1)$ representing the baseline, left and right
contexts, respectively. For all other hyperparameters, all contexts have the
same value. These values ensure that the prior over the hyperparameters
$(\mu_f, \sigma_f)$ has the mode at $(\mu_f^{(0)}, 1)$. We will show that the
choice of these hyperparameters affects learning rate, but not the final
learned magnitude \todo{Check this}.

@@

\section{Simulation results}
\subsection{Effects of observation noise on inference}
Observation noise refers to the noise on the position of the hand. The
generating process is a Gaussian with $\sigma = 0.1$, which is determined in
./code/adaptation/pars.py. However, the agent has a belief on this value, which
is fixed for the agent. This value (obs\_sd, which can be passed on
instanciation) can be used in lieu of an explicit $\Delta t$ parameter which
controls the size of the time step

\subsection{Parameter values to look into}
By visual inspection of the results of simulations, these are the parameter values that seem promising:

\begin{tabularx}{\textwidth}{
  >{\hsize=.2\hsize\linewidth=\hsize}X|
  >{\hsize=.1\hsize\linewidth=\hsize}X|
  >{\hsize=.1\hsize\linewidth=\hsize}X|
  l}
% {l|{\hsize=.4\hsize}X|{\hsize=0.3\hsize}X|{\hsize=0.3\hsize}X}
Agent & Obs noise & Cue noise & Notes \\ \hline \hline
LR    & 1.2       & 0.04      & Slow fake-context inference. Maybe the priors coming from the previous stage are messing things up. \\ \hline
1 & 1 & 1 & 1
\end{tabularx}

\section{Conclusions}

>>>>

\subsection{Left-right with fixed force value (LR)}
In this version, the force field is assumed to have a fixed value which the
agent tries to infer. The agent's uncertainty on this inference is reflected on
the parameters of the posterior over the force directly. For simplicity, we
assume that the priors (and posteriors) are normal with mean and standard
deviation to be updated at every time step. Therefore, the posterior over the
magnitude of the force for each context is given by:
\begin{equation}
q_t(\gamma) = N(\mu_{\gamma}, \sigma_\gamma)
\end{equation}
where $q_t(\gamma)$ is the posterior of the magnitude $\gamma$ of the force
field distribution after the observations at time $t$, and $\mu_\gamma$ and
$\sigma_\gamma$ are the inferred parameters of the distribution.

@@

\subsection{Left-right with unknown standard deviation (LRS)}
In this model, the force at each trial is assumed to be sampled from a normal
distribution and the mean of this distribution is inferred from the
observations, while the standard deviation is assumed to be known. The mean of
the force is assumed to also be normal with unknown mean and standard
deviation:
\begin{align}
  p(\gamma) &= N(\mu_t, \sigma) \\
  p(\mu_t) &= N(\mu_mu, \sigma_\mu)
\end{align}
In this manner, the uncertainty for this agent is at the level of the estimate
of the parameters of the force field, as opposed to being directly on the
force. Because the priors for $\mu_\mu$ are normal and the standard deviation
$\sigma$ (not $\sigma_mu$) is known, the update equations are given by:
\begin{align}
  \mu_\mu &= \frac{\sigma^2}{\sigma^2 + \sigma_\mu^2}\mu_\mu + \frac{\sigma_\mu^2}{\sigma^2 + \sigma_\mu^2} x \\
  \sigma_\mu &= \frac{\sigma^2\sigma_\mu^2}{\sigma^2 + \sigma_\mu^2}
\end{align}
where $x$ is the observation.

\subsection{Left-right with unknown mean and standard deviation (LRMS)}
In this version, we will assume that for each context, the agent's belief over
the magnitude of the force is given by a normal distribution:
\begin{equation}
p(\gamma) = N(\mu_f, \sigma_f) \label{eqn:data-dist}
\end{equation}
where $\mu_f$ and $\sigma_f$ are parameters to be estimated at each
trial. Before the experiment begins, the agent will have a prior distribution
over these parameters. A standard Bayesian approach is to choose NormalGamma
priors:
\begin{equation}
p(\mu_f, \sigma_f) = NG(\mu_0, \nu_0, \alpha_0, \beta_0)
\end{equation}
where $\mu_0, \nu_0, \alpha_0$ and $\beta_0$ are free hyperparameters of the
model. Because participants are told that there are three contexts (baseline,
left and right), we assume the following hyperparameter values:
\begin{align} \mu_f^{(0)} &= (0, -1, 1) \\
  \nu_f^{(0)} &= 0.1 \\
  \alpha_f^{(0)} &= 1 \\
  \beta_f^{(0)} &= 0.5
\end{align}
Note that $\mu_f^{(0)}$ is different for each context and is thus
provided as a vector $(0, -1, 1)$ representing the baseline, left and right
contexts, respectively. For all other hyperparameters, all contexts have the
same value. These values ensure that the prior over the hyperparameters
$(\mu_f, \sigma_f)$ has the mode at $(\mu_f^{(0)}, 1)$. We will show that the
choice of these hyperparameters affects learning rate, but not the final
learned magnitude \todo{Check this}.

@@

\section{Simulation results}
\subsection{Deadaptation and context inference}
During the deadaptation phase, not all parametrized agents detect the correct context. For each agent type (LR, LRS, LRMS), different parameter values allow the information from the predicted hand positions to overcome the information from the cue, which enables the correct identification of the current context.

It is unclear which parameter values lead to this, but, as expected, prediction noise (see XXX) and context noise (see XXX) play an important role. In particular, keeping the prediction noise below 0.2 seems to be necessary for the correct identification of the context, for all the used values of context noise. It could be good to check this.

\subsection{Adaptation}
Adaptation happens mostly very quickly for all agents. For the current $\Delta t = \dt$, adaptation happens within 20 to 30 time steps, although many times (depending on agent and parametrization) it happens much more quickly. For example, for the LR agent with prediction noise of 0.15, cue noise and context noise of 0, and assumed force variability of 0.25, within 15-20 time steps the adaptation is complete.
\section{Conclusions}
